A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-18 main.tex
Define substituition.

@@

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.

>>>>

In this section, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its defnition here.
Substituition $M[\alpha \mapsto \epsilon]$ is defined below.

\begin{align*}
    % \newcommand{\SB}{}
    (\lambda x:\tau.M)[\alpha \mapsto \epsilon] &= \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon] \\
    (M\ N)[\alpha \mapsto \epsilon] &= (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon]) \\
    (\TB_\beta M)[\alpha \mapsto \epsilon] &= \TB_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
    (\TBL_\beta M)[\alpha \mapsto \epsilon] &= \TBL_{\beta[\alpha \mapsto \epsilon]} M[\alpha \mapsto \epsilon] \\
    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M[\alpha \mapsto \epsilon] & (\text{if } \alpha \neq \beta) \\
    (\Lambda\beta.M)[\alpha \mapsto \epsilon] &= \Lambda\beta.M & (\text{if } \alpha = \beta) \\
    (M\ \epsilon)[\alpha \mapsto \epsilon] &= M[\alpha \mapsto \epsilon]\ \epsilon \\
    (\%_\beta M)[\alpha \mapsto \epsilon] &= \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon] 
\end{align*}

@@

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.
